Box

### 2021-10-04 MS/box.Rmd
Added ref to ARR main effects and interaction derivation in supplement

where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (e.g., mean CTmax) at temperature points $T_{1}$ and $T_{2}$.

@@

$$
\sigma^2_{AAR} = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{SD^2_{1}} {N_{1}} + \frac{SD^2_{2}} {N_{2}} \right)
$$

>>>>

where *T* stands for temperature in degrees Celsius and $T_{2} > T_{1}$, and $M_{1}$ and $M_{2}$ are the average physiological responses (e.g., mean CTmax) at temperature points $T_{1}$ and $T_{2}$. Many studies might manipulate multiple variables using a fully factorial design (e.g., temperature and pH), however, for simplicity we assume the study only manipulates temperature. In the supplement, we also show how to derive *ARR* from fully factorial studies (i.e., main effects and interactions).

@@

$$
\sigma^2_{ARR} = \left( \frac{1} {T_2 - T_1} \right)^2 
\left( \frac{SD^2_{1}} {N_{1}} + \frac{SD^2_{2}} {N_{2}} \right)
$$
